%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large George Baker}} & \href{mailto:georgestephenbaker@icloud.com}{georgestephenbaker@icloud.com} \\
  & \href{https://www.github.com/gsbaker}{github.com/gsbaker}
\end{tabular*}

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \textbf{Programming languages}: Ruby, Python, Javascript, Java, SQL \\
 \textbf{Frameworks}: Ruby on Rails, Django \\
 \textbf{Developer tools}: vim, tmux, git, docker


%-----------EXPERIENCE-----------------
\section{Experience}

      \textbf{FreeAgent} (Edinburgh, UK) \\
      \textit{Software Engineer, 2022—present} \\
      \textit{Intern, 2021} \\

      \begin{itemize}[noitemsep]
      \item Product engineer working with Ruby on Rails, \href{https://hotwired.dev}{Hotwire} on the front-end, and a MySQL database.
      \item Led work to support a new feature from GoCardless (a Direct Debit payment solution) in FreeAgent's invoicing functionality. 
      Responsibilities included initial discovery work, writing a tech spec, and breaking down work into user stories.
      \item Migrated legacy jQuery code for dynamic page updates to \href{https://turbo.hotwired.dev}{Turbo} (part of Hotwire library).
      \item Helped build one of FreeAgent's first paid add-ons: \href{https://www.freeagent.com/blog/introducing-smart-capture/}{Smart Capture}
      (feature that automatically extracts date and amount from a receipt). Contributions included adding support for bills and matched bank transactions.
      \item Won hack days founder’s award twice (for most project most beneficial to the business) demoing an MVP of typeahead search for email 
      templates, and a better onboarding journey for creating your first invoice.
      \end{itemize}


%-----------PROJECTS-----------------
\section{Projects}

\textbf{\href{https://reflet.io}{reflet.io}} \\
\textit{Source code: \href{https://github.com/gsbaker/reflet}{github.com/gsbaker/reflet}} \\

\begin{itemize}[noitemsep]
\item Web application that enables therapists to easily collaborate with their clients (no customers yet, still in build).
\item Features include anxiety questionnaire assignments, sharing attachments, writing up notes following a session, and \textit{"needs records"}.
\item Created with Ruby on Rails, Hotwire, SQLLite, and deployed with \href{https://kamal-deploy.org}{Kamal}.
\end{itemize}


%-----------EDUCATION-----------------
\section{Education}

\textbf{Computer Science BSc} (University of Birmingham) \\

\begin{itemize}[noitemsep]
\item Researched conformity to social pressure in online behaviour as part of final year undergraduate project.
\item Modules included \textit{Principles of Programming, Functional Programming (Haskell), Systems Programming (C/C++), Human Computer Interaction}
\end{itemize}

%-----------HOBBIES-----------------
\section{Hobbies}

\begin{itemize}[noitemsep]
\item Photography
\item Tennis
\item Playing Mario Kart
\item Listening to music and podcasts
\end{itemize}

%-------------------------------------------
\end{document}
