%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 10pt]{letter}

\usepackage{hyperref}
\usepackage[top=0.75in,bottom=0.75in,left=1in,right=1in]{geometry} % Added for margin control


% Name of sender
\name{George Baker}

% Signature of sender
\signature{George Baker}

% Address of sender
\address
{
    Edinburgh, UK
}

%-----------------------------------------------------------------------------%

\begin{document}

% Name and address of receiver
\begin{letter}{}

% Opening statement
\opening{Dear 37signals,}

% Letter body

My name is George and I am writing to apply for the position of Junior Rails Programmer.

I've been working for around \emph{two and a half years} as a Rails Programmer at
\href{https://www.freeagent.com}{FreeAgent}, an accountancy platform for small businesses in the UK.

Here's some of the things I've worked on recently:
\begin{itemize}
\item Diagnosing a database deadlock issue on our invoicing API (caused by too many
overlapping requests) and working with a more senior programmer to fix it
\item Leading work to support a new GoCardless feature that automatically retries failed Direct Debit
payments within FreeAgent's invoicing functionality
\item Dynamically updating the "Matched transaction" status for a newly
uploaded receipt using Turbo based polling
\item Updating the contact field on our web forms to use an
\emph{'autocomplete'} combobox
field rather than a traditional HTML select (much easier to use, especially for customers
with a large amount of contacts)

\end{itemize}

Although I've learnt a lot at FreeAgent, I don't think I've reached my ceiling
there. I think I can become an excellent programmer, and I think 37signals has
the right people to help make that happen. Sure, when I arrive, I'll
probably make some mistakes that'll make the other programmers cringe, but I'm
a very quick learner, and I put \emph{a lot} of effort into my work.

I'm the kind of person that obsesses over writing clean, beautiful code, not
someone who's satisfied with something that \emph{'just works'}.

Furthermore, I think I'd be a good fit for 37signals since I'm used to working
remotely, in fact, I find I'm much more productive doing so. 
I'm also pretty self-sufficient at work; I like to just get on with things :).

In addition to my professional work experience, I'm also working on a web
application to help therapists collaborate with their clients:
\href{https://reflet.io}{reflet.io}. I've been
writing the application with Rails (source code
\href{https://github.com/gsbaker/reflet}{here}), and I've been taking
advantage of some of the newer tools, e.g., Kamal for deploying to
a DigitalOcean droplet in the cloud. 

A little about George the human: I live in beautiful Edinburgh, I drink a lot of early
grey tea, and I enjoy running (although not when it's \emph{'chucking it down'} as we
like to say).

Thanks for reading my (non AI generated) cover letter! I'd be very happy to
chat further, or answer any questions. If you think I'm not such a great fit,
then I wish you all the best in finding the right candidate.

% Closing statement
\closing{Yours sincerely,}

\end{letter}
\end{document}
%-----------------------------------------------------------------------------%
